How to Not write Virtual Machines for Dynamic Languages

### 2007-05-27 talk/dyla2007/dyla.tex
Fix an XXX.

\item
\emph{A single unified implementation base:} The higher level of abstraction
mentioned in the last point also helps to reduce the number of implementations
of the language. Since the implementation on top of an OO VM is more abstract
it is also easier to modify and to extend. XXX somewhat vague point
\end{itemize}

>>>>

\item
\emph{A single unified implementation base:} The .NET and Java VMs are trying
to position themselves as all-encompassing platforms; if one succeeds, then
implementations of the dynamic language for other platforms might no longer
be required.
\end{itemize}
